### 2023-01-14 README.Rmd
make `resolve` disable Enhances by default fix #3

The goal of gran is to ...

@@

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

@@

This is a basic example which shows you how to solve a common problem:

```{r example}
library(gran)
## basic example code
```

What is special about using `README.Rmd` instead of just `README.md`? You can include R chunks like so:

```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.

>>>>

The goal of gran (gran: R anachronism nullifier) [^gesis] is to obtain the dependency graph of an R package at a specific time point.

@@

``` r
remotes::install_github("GESIS-Methods-Hub/gran")
```

@@

To obtain the dependency graph of an R package, use `resolve`

```{r example}
library(gran)
rtoot_graph <- resolve(pkg = "rtoot", snapshot_date = "2022-12-31")
rtoot_graph
```

---

[^gesis]: Actually, it stands for "GESIS R Archive Network".
